DNA Methylation Analysis

### 2023-02-16 DNA-methylation.Rmd
meth ds file conversion

>>>>

It is often useful to sort files for downstream analysis (eg methylkit, IGV)

```
# Sort files for methylkit and IGV

find *.bam | \
xargs basename -s .bam | \
xargs -I{} ${samtools} \
sort --threads 28 {}.bam \
-o {}.sorted.bam

# Index sorted files for IGV

find *.sorted.bam | \
xargs basename -s .sorted.bam | \
xargs -I{} ${samtools} \
index -@ 28 {}.sorted.bam
```
